A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-06 manuscript.Rmd
add all abbrevations closes #116

---
title: A Hitchhiker's Guide to Reproducible Research in R
author:
  - name: Aaron Peikert
    affil: 1, *
    orcid: 0000-0001-7813-818X
  - name: Caspar J. Van Lissa
    affil: 2, 3
    orcid: 0000-0002-0808-5024
  - name: Andreas M. Brandmaier
    affil: 1, 4
    orcid: 0000-0001-8765-6982
affiliation:
  - num: 1
    address: |
      Center for Lifespan Psychology---Max Planck Institute for Human Development
      Lentzeallee 94, 14195 Berlin, Germany
  - num: 2
    address: |
      Department of Methodology & Statistics---Utrecht University faculty of Social and Behavioral Sciences, Utrecht, Netherlands
  - num: 3
    address: |
      Open Science Community Utrecht, Utrecht, Netherlands
  - num: 4
    address: |
      Max Planck UCL Centre for Computational Psychiatry and Ageing Research
      Berlin, Germany and London, UK
# firstnote to eighthnote
correspondence: |
  peikert@mpib-berlin.mpg.de
journal: psych
type: tutorial
status: submit
bibliography: temp.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.Rmd'))))`"
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  The authors received no financial support for the research, authorship, and/or publication of this article.
authorcontributions: |
  Aaron Peikert took the lead in writing and provided the initial draft of the manuscript.
  Andreas Brandmaier and Caspar J. Van Lissa contributed further ideas, critical feedback, and revisions of the original manuscript.
  Furthermore, we would like to thank Maximilian Stefan Ernst (not an author) for his contributions to the code for the simulation study.
conflictsofinterest: |
  The authors declare no conflict of interest.
abbreviations:
  - short: GUI
    long: Graphical User Interface
  - short: CLI
    long: Comand Line Interface
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
    - rticles
    - moments
    - report
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
  data:
    - data/simulation_results.csv
output:
  bookdown::markdown_document2:
    base_format: rticles::mdpi_article
header-includes:
   - \usepackage[labelformat=empty]{caption}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}, numbers=left}
---

@@

Dynamic document generation fuses both steps and can be traced back to @knuthCWEBSystemStructured, who put it this way: "The main idea is to regard a program as a communication to human beings rather than as a set of instructions to a computer."
**R Markdown** uses Markdown for writing the text and R (or other programming languages) for the analysis.
Markdown is a lightweight text format in plain text with minimal reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing.
It is highly fool-proof (unlike, for example, LaTeX), works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest using Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles], and presentations[@revealjs] or even your CV [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks (in fact, arbitrary computer code; see @riedererChapter15Other) into a Markdown document.
Upon rendering the document, the code blocks are executed, and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).

>>>>

---
title: A Hitchhiker's Guide to Reproducible Research in R
author:
  - name: Aaron Peikert
    affil: 1, *
    orcid: 0000-0001-7813-818X
  - name: Caspar J. Van Lissa
    affil: 2, 3
    orcid: 0000-0002-0808-5024
  - name: Andreas M. Brandmaier
    affil: 1, 4
    orcid: 0000-0001-8765-6982
affiliation:
  - num: 1
    address: |
      Center for Lifespan Psychology---Max Planck Institute for Human Development
      Lentzeallee 94, 14195 Berlin, Germany
  - num: 2
    address: |
      Department of Methodology & Statistics---Utrecht University faculty of Social and Behavioral Sciences, Utrecht, Netherlands
  - num: 3
    address: |
      Open Science Community Utrecht, Utrecht, Netherlands
  - num: 4
    address: |
      Max Planck UCL Centre for Computational Psychiatry and Ageing Research
      Berlin, Germany and London, UK
# firstnote to eighthnote
correspondence: |
  peikert@mpib-berlin.mpg.de
journal: psych
type: tutorial
status: submit
bibliography: temp.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.Rmd'))))`"
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  The authors received no financial support for the research, authorship, and/or publication of this article.
authorcontributions: |
  Aaron Peikert took the lead in writing and provided the initial draft of the manuscript.
  Andreas Brandmaier and Caspar J. Van Lissa contributed further ideas, critical feedback, and revisions of the original manuscript.
  Furthermore, we would like to thank Maximilian Stefan Ernst (not an author) for his contributions to the code for the simulation study.
conflictsofinterest: |
  The authors declare no conflict of interest.
abbreviations:
  - short: PAC
    long: Preregistration as 
  - short: Gb
    long: Gigabyte
  - short: Kb
    long: Kilobyte
  - short: GUI
    long: Graphical User Interface
  - short: CLI
    long: Comand Line Interface
  - short: CRAN
    long: Comprehensive R Archive Network
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
    - rticles
    - moments
    - report
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
  data:
    - data/simulation_results.csv
output:
  bookdown::markdown_document2:
    base_format: rticles::mdpi_article
header-includes:
   - \usepackage[labelformat=empty]{caption}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}, numbers=left}
---

@@

Dynamic document generation fuses both steps and can be traced back to @knuthCWEBSystemStructured, who put it this way: "The main idea is to regard a program as a communication to human beings rather than as a set of instructions to a computer."
**R Markdown** uses Markdown for writing the text and R (or other programming languages) for the analysis.
Markdown is a lightweight text format in plain text with minimal reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing.
It is highly fool-proof (unlike, for example, LaTeX), works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest using Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles], and presentations[@revealjs] or even your résumé [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks (in fact, arbitrary computer code; see @riedererChapter15Other) into a Markdown document.
Upon rendering the document, the code blocks are executed, and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).
